---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse    = TRUE,
  comment     = "#>",
  fig.path    = "man/figures/README-",
  out.width   = "40%",
  eval        = TRUE
)
```

# cdssr

<!-- badges: start -->
[![Dependencies](https://img.shields.io/badge/dependencies-9/02-orange?style=flat)](#)
[![License: MIT](https://img.shields.io/badge/License-MIT-yellow.svg)](https://choosealicense.com/licenses/mit/)
<!-- badges: end -->

<div align="left">

  <p align="left">
    <a href="https://dwr.state.co.us/Tools"><strong>« CDSS »</strong></a>
    <br />
    <a href="https://dwr.state.co.us/Rest/GET/Help">CDSS API</a>
  </p>
</div>

<hr>

The goal of `cdssr` is to provide functions that help R users to navigate, explore, and make requests to the [CDSS REST API web service](https://dwr.state.co.us/Rest/GET/Help). 

The Colorado's Decision Support Systems (CDSS) is a water management system created and developed by the [Colorado Water Conservation Board (CWCB)](https://cwcb.colorado.gov/) and the [Colorado Division of Water Resources (DWR)](https://dwr.colorado.gov/). 

Thank you to those at CWCB and DWR for providing an accessible and well documented REST API! 

<hr>

## Installation

You can install the development version of `cdssr` from [GitHub](https://github.com/) with:

```{r, eval=FALSE, echo=TRUE}
# install.packages("devtools")
devtools::install_github("anguswg-ucsb/cdssr")
```

## Browse avaliable endpoints

To browse all the available endpoints shown [here](https://dwr.state.co.us/Rest/GET/Help) use `browse_api()`.

```{r, eval=TRUE, echo=TRUE}
# Load package
library(cdssr)
```

```{r browse_api_ex, eval=TRUE, echo=TRUE}
# View the catalog of avaliable endpoints
catalog <- cdssr::browse_api()

catalog
```

<br>

## View the return fields
Use `preview_endpoint()` Inspect what fields will be returned for a given endpoint by entering a `endpoint_url` (a column in the `browse_api()` output pointing to the endpoints help page)
```{r return_fields_ex, eval=TRUE, echo=TRUE}
# Return expected data fields for a given endpoint
return_fields <- cdssr::preview_endpoint(endpoint_url = catalog$endpoint_url[3])

return_fields
```

<br>

## Retrieve Telemetry station timeseries data 
Use `get_` function to make requests to the CDSS API and return the results in a tidy dataframe
```{r get_ts, eval=TRUE, echo=TRUE}
# Daily discharge at "CLAFTCCO" telemetry station
discharge_ts <- cdssr::get_telemetry_ts(
                      abbrev              = "CLAFTCCO",
                      parameter           = "DISCHRG",
                      start_date          = "2015-01-01",
                      end_date            = "2022-01-01",
                      timescale           = "day",
                      include_third_party = TRUE
                               )

head(discharge_ts, 10)
```

And a plot of the daily discharge...
```{r plot_ts, eval=TRUE, echo=TRUE, fig.align='center', out.width='100%'}
# Plot daily discharge at "CLAFTCCO"
plot(discharge_ts$value~discharge_ts$datetime, type = "l")
```


<br>

## Retrieve groundwater well data
The `get_groundwater()` function lets users make get requests to the various CDSS API groundwater endpoints using the **type** parameter.

Groundwater endpoints:

  - [api/v2/groundwater/waterlevels/wellmeasurements](https://dwr.state.co.us/Rest/GET/Help/Api/GET-api-v2-groundwater-waterlevels-wellmeasurements)
  - [api/v2/groundwater/waterlevels/wells](https://dwr.state.co.us/Rest/GET/Help/Api/GET-api-v2-groundwater-waterlevels-wells)
  - [api/v2/groundwater/geophysicallogs/wells](https://dwr.state.co.us/Rest/GET/Help/Api/GET-api-v2-groundwater-geophysicallogs-wells)

```{r get_gw, eval=TRUE, echo=TRUE}
# Use type = "wellmeasurements" to request wellmeasurements endpoint (api/v2/groundwater/waterlevels/wellmeasurements)
well_measure <- cdssr::get_groundwater(
  type    = "wellmeasurements",
  wellid  = 1274
  )

head(well_measure, 10)
```

And a plot of the depth to water over time...
```{r plot_gw, eval=TRUE, echo=TRUE, fig.align='center', out.width='100%'}
# plot depth to water
plot(well_measure$depth_to_water~well_measure$datetime, type = "l")
```

<br>
<br>

> **More functions for more endpoints coming soon!**










